\chapter {Conclusion}

In this chapter, we conclude the work has been done in the research project and all tasks that have been accomplished.

\section{Summary}
During the research project, We aimed to implement a real solution leveraging the blockchain features such as decentralization and data immutability.
In addition, Providing a solution for a real problem like Fake news. As Fake news in the digital era is one of the latest issues that has raised many concerns and has many negative effects for instance, biasing the public opinion, spreading the hate speech and destroying innocent people's reputation. \\ 

\noindent We started by studying the blockchain and hyperledger fabric. We designed a case study scenario for a mobile application that incents users to share and rank stories and storing them on the blockchain. Hyperledger fabric was used as a permissioned blockchain that restricting the access into the network and only the verified entities could participate. \\ 
 
\noindent We built a fully functioned development network using Docker containers and adopt one of the provided node.js APP, which abstracts the whole network and exposes Rest APIs for different chaincode operations on the hyperledger fabric,The node.js App also serves as a back-end to the whole infrastructure after highly modifying the code to match our case. 
We built a simple Xampp development server in order to allow the users to register in a traditional way using email and password, Furthermore we introduced an efficient way for storing data on the blockchain by storing only the hash of the media files, and serving the media files as content delivery network CDN approach for more efficient, low latency and high performance. 
In addition, We implemented a score and reputation system using the chaincode and location trustworthiness.  We designed an Android application for the end user that facilitates the interaction and allows different operations. The application designed to be user-friendly, self-explanatory and easy to use. Finally, we introduced a modular design thus more features with the minimum required modifications will be easy introduced and integrated into an inter-operable environment.